%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Hyungtae Lim} \\ \vspace{1pt}
    \small
    \href{mailto:shapelim@mit.edu}{\underline{shapelim@mit.edu}} $|$
    \href{https://limhyungtae.github.io/hyungtae-lim/}{\underline{limhyungtae.github.io}} $|$
    \href{https://linkedin.com/in/hyungtae-lim}{\underline{linkedin.com/in/hyungtae-lim}} $|$
    \href{https://github.com/limhyungtae}{\underline{github.com/limhyungtae}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Korea Advanced Institute of Science and Technology (KAIST)}{Daejeon, Korea}
      {Ph.D. in Electrical Engineering and Robotics Program}{Mar. 2020 -- Feb. 2023}
      \resumeItemListStart
        \resumeItem{Dissertation: ``Robust LiDAR SLAM for Autonomous Vehicles Leveraging Ground Segmentation''}
        \resumeItem{Advisor: Prof. Hyun Myung}
      \resumeItemListEnd
    \resumeSubheading
      {Korea Advanced Institute of Science and Technology (KAIST)}{Daejeon, Korea}
      {M.S. in Electrical Engineering and Robotics Program}{Mar. 2018 -- Feb. 2020}
    \resumeSubheading
      {Korea Advanced Institute of Science and Technology (KAIST)}{Daejeon, Korea}
      {B.S. in Mechanical Engineering}{Mar. 2013 -- Aug. 2018}
      \resumeItemListStart
        \resumeItem{Dean's List in Mechanical Engineering (GPA 4.23/4.3) -- Fall 2015}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Postdoctoral Associate}{Apr. 2024 -- Present}
      {SPARK Lab, MIT (Advisor: Prof. Luca Carlone)}{Cambridge, MA}
      \resumeItemListStart
        \resumeItem{Conduct research on multi-robot/-session autonomous mapping in complex urban environments.}
        \resumeItem{Guide and supervise graduate and undergraduate students in research papers and thesis projects.}
        \resumeItem{Maintainer of TEASER++ (2.1K $\bigstar$), Hydra (773 $\bigstar$), KISS-Matcher (643 $\bigstar$), VGGT-SLAM (882 $\bigstar$).}
      \resumeItemListEnd

    \resumeSubheading
      {Postdoctoral Fellow}{Mar. 2023 -- Mar. 2024}
      {Urban Robotics Lab, KAIST (Advisor: Prof. Hyun Myung)}{Daejeon, Korea}
      \resumeItemListStart
        \resumeItem{Research on LiDAR and vision-based localization and mapping for autonomous systems.}
        \resumeItem{Developed deep learning models for robust robot perception in dynamic environments.}
      \resumeItemListEnd

    \resumeSubheading
      {Visiting Scholar}{Nov. 2022 -- Feb. 2023}
      {StachnissLab, University of Bonn (Advisor: Prof. Cyrill Stachniss)}{Bonn, Germany}
      \resumeItemListStart
        \resumeItem{Collaborated on an improved method for static map building in dynamic scenes.}
        \resumeItem{Paper accepted at RSS 2023: \textit{ERASOR2: Instance-Aware Robust 3D Mapping of the Static World}.}
      \resumeItemListEnd

    \resumeSubheading
      {Research Intern}{Apr. 2022 -- Sep. 2022}
      {NAVER LABS}{Gyeonggi-Do, Korea}
      \resumeItemListStart
        \resumeItem{Worked on robust global registration using 3D point cloud data from LiDAR sensors.}
        \resumeItem{Paper accepted at IEEE ICRA 2023: \textit{ORORA: Outlier-Robust Radar Odometry}.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------SELECTED PUBLICATIONS-----------
\section{Selected Publications}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{KISS-Matcher} $|$ \emph{IEEE ICRA 2025}}{2025}
          \resumeItemListStart
            \resumeItem{H. Lim et al., ``KISS-Matcher: Fast and Robust Point Cloud Registration Revisited.''}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{VGGT-SLAM} $|$ \emph{NeurIPS 2025} (882 $\bigstar$)}{2025}
          \resumeItemListStart
            \resumeItem{D. Maggio, H. Lim, and L. Carlone, ``VGGT-SLAM: Dense RGB SLAM Optimized on the SL(4) Manifold.''}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{BUFFER-X} $|$ \emph{IEEE/CVF ICCV 2025} (243 $\bigstar$)}{2025}
          \resumeItemListStart
            \resumeItem{M. Seo, H. Lim et al., ``BUFFER-X: Towards Zero-Shot Point Cloud Registration in Diverse Scenes.''}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{ERASOR2} $|$ \emph{RSS 2023}}{2023}
          \resumeItemListStart
            \resumeItem{H. Lim et al., ``ERASOR2: Instance-Aware Robust 3D Mapping of the Static World in Dynamic Scenes.''}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Quatro++} $|$ \emph{IJRR 2023}}{2023}
          \resumeItemListStart
            \resumeItem{H. Lim et al., ``Quatro++: Robust Global Registration Exploiting Ground Segmentation for Loop Closing.''}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Patchwork++} $|$ \emph{IEEE/RSJ IROS 2022} (842 $\bigstar$)}{2022}
          \resumeItemListStart
            \resumeItem{S. Lee, H. Lim, and H. Myung, ``Patchwork++: Fast and Robust Ground Segmentation.''}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{ERASOR} $|$ \emph{IEEE RA-L w/ ICRA 2021} (494 $\bigstar$)}{2021}
          \resumeItemListStart
            \resumeItem{H. Lim et al., ``ERASOR: Egocentric Ratio of Pseudo Occupancy-Based Dynamic Object Removal.''}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------HONORS \& AWARDS-----------
\section{Honors \& Awards}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{2025} -- IEEE ICRA'25 Outstanding Reviewer Award (5 awardees out of 7,641 reviewers) \\
     \textbf{2024} -- RSS Pioneers 2024 (30 selected out of 202 candidates) \\
     \textbf{2024} -- 1st Prize, HILTI SLAM Challenge in IEEE ICRA'24 \\
     \textbf{2023} -- Best Paper Award, IEEE RA-L (5 of 1,100 papers) \\
     \textbf{2023} -- 1st Prize, HILTI SLAM Challenge in IEEE ICRA'23 (63 international teams) \\
     \textbf{2023} -- CES'23 Innovation Award (via technology transfer with HILLS Robotics) \\
     \textbf{2022} -- 2nd Cash Prize, HILTI SLAM Challenge in IEEE ICRA'22 \\
     \textbf{2020} -- Student Best Paper Award, ICCAS
    }}
 \end{itemize}


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming}{: C++, Python, CUDA, CMake} \\
     \textbf{Frameworks \& Tools}{: ROS/ROS2, PyTorch, OpenCV, Git, Docker} \\
     \textbf{Research Areas}{: SLAM, 3D LiDAR, Point Cloud Registration, Ground Segmentation, Sensor Fusion, Deep Learning} \\
     \textbf{Languages}{: Korean (Native), English (Fluent)}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
